Intentional release of native species undermines ecological stability

### 2022-09-22 rmd/supporting_info.Rmd
Update supporting_info.Rmd

We subsequently analyzed a whole community model with $10$ species using important parameter combinations identified in the two-species simulation: intrinsic growth of enhanced species ($r_1 =$ `r unique(list_param[[1]]$r1)`), average strength of interspecific competition ($\bar{\alpha}=$ `r unique(list_param[[1]]$alpha)`), carrying capacity ($K=$ `r unique(list_param[[1]]$k)`), and relative fitness of captive-bred individuals ($f_R=$ `r unique(list_param[[1]]$phi)`). We confirmed that these parameters are influential in the ten-species community model via sensitivity analysis (**Table S2-S4**). Meanwhile, we fixed values of the following parameters: the number of species ($S=$ `r unique(list_param[[1]]$n_species)`), maximum intrinsic growth rate of unenhanced species ($r_{max}=$ `r unique(list_param[[1]]$r_max)`), and environmental stochasticity ($\sigma_{\epsilon}=$ `r unique(list_param[[1]]$sd_env)`). This simulation setup resulted in `r nrow(list_param[[1]])` sets of parameter combinations.

@@

## conditional text
c_text <- case_when(name == "all" ~ "whole community",
                    name == "masu" ~ "masu salmon",
                    name == "other" ~ "unenhanced species")

@@

for(i in seq_len(length(df_est))) {

  knit_chunk <- paste0("## Table S", i + j, " Parameter estimates for the regression model (", c_text[i], ") \n",
                       table_legend,
                       "\n```{r table_s", i + j,"}
                       \n\n
                       kable(df_est[[",i,"]],
                             align = c(rep('l', 3), rep('c', 4)),
                             format = 'markdown')
                       \n\n
                       ```\n",
                       "\n\\pagebreak\n")

>>>>

We subsequently analyzed a whole community model with $10$ species using important parameter combinations identified in the two-species simulation: intrinsic growth of enhanced species ($r_1 =$ `r unique(list_param[[2]]$r1)`), average strength of interspecific competition ($\bar{\alpha}=$ `r unique(list_param[[2]]$alpha)`), carrying capacity ($K=$ `r unique(list_param[[2]]$k)`), and relative fitness of captive-bred individuals ($f_R=$ `r unique(list_param[[2]]$phi)`). We confirmed that these parameters are influential in the ten-species community model via sensitivity analysis (**Table S2-S4**). Meanwhile, we fixed values of the following parameters: the number of species ($S=$ `r unique(list_param[[2]]$n_species)`), maximum intrinsic growth rate of unenhanced species ($r_{max}=$ `r unique(list_param[[2]]$r_max)`), and environmental stochasticity ($\sigma_{\epsilon}=$ `r unique(list_param[[2]]$sd_env)`). This simulation setup resulted in `r nrow(list_param[[2]])` sets of parameter combinations.

@@

## conditional text
c_text <- case_when(group == "all" ~ "whole community",
                    group == "masu_salmon" ~ "masu salmon",
                    group == "other" ~ "unenhanced species")

@@

for(i in seq_len(length(list_reg))) {

  knit_chunk <- paste0("## Table S", i + j, " Parameter estimates for the regression model (", c_text[i], ") \n",
                       table_legend,
                       "\n```{r table_s", i + j,"}
                       \n\n
                       kable(list_reg[[",i,"]],
                             align = c(rep('l', 3), rep('c', 4)),
                             format = 'markdown')
                       \n\n
                       ```\n",
                       "\n\\pagebreak\n")
